Quantum Computing and its Implications on Digital Security

### 2022-01-08 paper.tex
feat: Final corrections

\begin{section}{Related Work}
Prashant writes about the limitations of classical computers and how quantum computers can be realized \cite{prashant}. 
Their brief explanations on different realizations of quantum computers is introducing the reader to several related research areas on a high level.

Providing detailed examples of the workings of Shor's and Grover's algorithm are Bone and Castro in their overview of quantum computing \cite{Bone}.

Vedral and Planio provide an especially interesting and detailed explanation of ion trap quantum computers in their paper \cite{2008}.

@@

Diving a little bit deeper, Mavroeidis et al. introduce the reader to present cryptography algorithms, how they are vulnerable to quantum computers and their main topic, post quantum security \cite{DBLP:journals/corr/abs-1804-00200}.

@@

\begin{section}{Quantum Computers}
Quantum computers utilize qubits to represent information. 
Instead of working with a stream of electrical or optical signals representing 1s and 0s, 
quantum computers utilize qubits, which can represent various combinations of 1s and 0s at the same time. 
This effect is called superposition. To put qubits into superposition, 
researchers manipulate qubits in different ways. As quantum computing is based on quantum mechanics and hence has to obey to the same laws, 
a measurement determines the state of a qubit. Once qubits are measured, 
its quantum state immediately collapses to either 1 or 0 and its state of superposition is lost.

@@

\begin{section}{Experimental Realizations of Quantum Computers}

@@

Solid state NMRs differ from LSNMRs in that SSSNMRs provide a solid state sample.
This has many advantages such as lack of molecular diffusion coherence and lower temperatures, as well as the more precise localization of qubits using crystal structures.
In SSNMRs, qubits can be measured individually, same as in the ion trap,
instead of having to measure an ensemble of molecules as in LSNMR.

@@

\begin{itemize}
    \item Often, as e.g. in the Josephson junction quantum computer, extremely low temperatures are needed. These have to be achieved at a reasonable cost. Using e.g. laser cooling is one approach in quantum computing. The concept of laser cooling was proposed by Steven Chu, Claude-Cohen-Tannoudji and William D. Phillips who got awarded the Nobel prize for their research in the develoment of methods to cool and trap atoms with laser light.
    \item Quantum algorithms have probabilistic characteristics. 
    This implies that in a single operation a quantum computer returns multiple solutions, each of those solutions with an assigned probability, where only one can be correct. 
    Figuring out the correct answer reduces the potential speed of quantum computers.
    \item Qubits are prone to errors earlier introduced as noise. 
    Noise can be caused e.g. by heat or noise in the environment. 
    As in classical computing, noise can lead to bit-flips. There are approached in "quantum error correction" to deal with these errors. 
    One of those approaches is to use the "bit flip code" in which a total of 3 qubits are needed to result in 1 correct bit using quantum entanglement.  
    \item Increasing the number of qubits in a processor is fundamental. The more qubits in a processor, the more logical qubits can be used. More qubits also lead to less errors since methods for error correction can be used more effectively.
    \item Decoherence leads to qubits retaining their quantum state only for a short period of time. 
    According to Mavroeidis \cite[p.3]{DBLP:journals/corr/abs-1804-00200} The longest time qubits remained in superposition so far was set by Australian researchers at the University of New South Wales. 
    Their qubits remained in superposition for a total of 35 seconds.
\end{itemize}

@@

% Research for this paragraph and add some more post quantum crypto examples
\begin{section}{Post Quantum Cryptography}
Post Quantum Cryptography describes algorithms that are secure against quantum computing and conventional computers. To make sure that an algorithm is quantum secure, there are generally two approaches: 
\begin{subsection}{Improve Current Security Mechanisms}    
Improving current security mechanisms by increasing the key length from 128 bits to 256 bits squares the number of possible permutations a quantum computer has to search using Grover's algorithm. 
The speedup Grover's algorithm provdides is not that efficient as that it could crack this key in a feasible amount of time.
\end{subsection}

>>>>

\begin{section}{Related Work}
Prashant writes about the limitations of classical computers and how quantum computers can be realized \cite{prashant}. 
Their explanations on different realizations of quantum computers are introducing the reader to several related research areas on a high level.

Providing examples of the workings of Shor's and Grover's algorithm are Bone and Castro in their overview of quantum computing \cite{Bone}.

Vedral and Planio provide a detailed explanation of ion trap quantum computers in their paper about the fundamentals of quantum computing \cite{2008}.

@@

Mavroeidis et al. introduce the reader to present cryptography algorithms, how they are vulnerable to quantum computers and their main topic, post quantum security \cite{DBLP:journals/corr/abs-1804-00200}.

@@

\begin{section}{Quantum Computers}
Quantum computers utilize qubits to represent information. 
Instead of working with classical bits representing 1s and 0s, 
quantum computers utilize qubits, which can represent various combinations of 1s and 0s at the same time. 
This effect of qubits representing multiple states at the same time is called superposition. To put qubits into superposition, 
researchers manipulate qubits in different ways. As quantum computing is based on quantum mechanics and hence has to obey to the same laws, 
a measurement determines the state of a qubit. Once qubits are measured, 
its quantum state immediately collapses to either 1 or 0 and its state of superposition is lost.

@@

\begin{section}{Realizations of Quantum Computers}

@@

Solid state NMRs differ from LSNMRs in that SSSNMRs provide a sample in solid state.
This has many advantages such as being able to work using lower temperatures as well as the more precise localization of qubits using crystal structures.
In SSNMRs, qubits can be measured individually, same as in the ion trap,
instead of having to measure an ensemble of molecules as in LSNMRs.

@@

\begin{itemize}
    \item Often, as e.g. in the Josephson junction quantum computer, extremely low temperatures are required. These have to be achieved at a reasonable cost. Using e.g. laser cooling is one approach in quantum computing. The concept of laser cooling was proposed by Steven Chu, Claude-Cohen-Tannoudji and William D. Phillips who got awarded the Nobel prize for their research in the develoment of methods to cool and trap atoms with laser light.
    \item Quantum algorithms have probabilistic characteristics. 
    This implies that in a single operation a quantum computer returns multiple solutions, each of those solutions with an assigned probability, where only one can be correct. 
    Figuring out the correct answer reduces the potential speed of quantum computers.
    \item Qubits are prone to errors earlier introduced as noise. 
    Noise can be caused e.g. by heat or noise in the environment. 
    As in classical computing, noise can lead to bit-flips. There are approaches in "quantum error correction" to deal with these errors. 
    One of those approaches is to use the "bit flip code" in which a total of 3 qubits are needed to result in 1 correct bit using quantum entanglement.  
    \item Increasing the number of qubits in a processor is fundamental. The more qubits in a processor, the more logical qubits can be used. More qubits also lead to less errors since methods for error correction can be used more effectively.
    \item Decoherence leads to qubits retaining their quantum state only for a short period of time. 
    According to Mavroeidis \cite[p.3]{DBLP:journals/corr/abs-1804-00200} The longest time qubits remained in superposition so far was set by Australian researchers at the University of New South Wales. 
    Their qubits remained in superposition for a total of 35 seconds.
\end{itemize}

@@

\begin{section}{Post Quantum Cryptography}
Post Quantum Cryptography describes algorithms that are secure against quantum computing and conventional computers. To make sure that an algorithm is quantum secure, there are generally two approaches: 
\begin{subsection}{Improve Current Security Mechanisms}    
Improving current security mechanisms by increasing the key length from 128 bits to 256 bits squares the number of possible permutations a quantum computer has to search using Grover's algorithm. 
The speedup Grover's algorithm provdides is not that efficient as that it could crack this key in a feasible amount of time.
\end{subsection}
